PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-07-01 manuscript.natcomm.tex
Improved bibliography.

\bibitem[Lin et~al.(2017)Lin, Doll{\'a}r, Girshick, He, Hariharan, and
  Belongie]{linFeaturePyramidNetworks2017}
Tsung-Yi Lin, Piotr Doll{\'a}r, Ross Girshick, Kaiming He, Bharath Hariharan,
  and Serge Belongie.
\newblock Feature {{Pyramid Networks}} for {{Object Detection}}, April 2017.

\bibitem[Lin et~al.(2018)Lin, Goyal, Girshick, He, and
  Doll{\'a}r]{linFocalLossDense2018}
Tsung-Yi Lin, Priya Goyal, Ross Girshick, Kaiming He, and Piotr Doll{\'a}r.
\newblock Focal {{Loss}} for {{Dense Object Detection}}, February 2018.

\bibitem[Liu et~al.(2021)Liu, Sharma, Park, Kenesei, Miceli, Almer, Kettimuthu,
  and Foster]{liuBraggNNFastXray2021}
Zhengchun Liu, Hemant Sharma, Jun-Sang Park, Peter Kenesei, Antonino Miceli,
  Jonathan Almer, Rajkumar Kettimuthu, and Ian Foster.
\newblock {{BraggNN}}: {{Fast X-ray Bragg Peak Analysis Using Deep Learning}}.
\newblock \emph{arXiv:2008.08198 [cs, eess]}, June 2021.

@@

\bibitem[Oktay et~al.(2018)Oktay, Schlemper, Folgoc, Lee, Heinrich, Misawa,
  Mori, McDonagh, Hammerla, Kainz, Glocker, and
  Rueckert]{oktayAttentionUNetLearning2018}
Ozan Oktay, Jo~Schlemper, Loic~Le Folgoc, Matthew Lee, Mattias Heinrich,
  Kazunari Misawa, Kensaku Mori, Steven McDonagh, Nils~Y. Hammerla, Bernhard
  Kainz, Ben Glocker, and Daniel Rueckert.
\newblock Attention {{U-Net}}: {{Learning Where}} to {{Look}} for the
  {{Pancreas}}, May 2018.

@@

\bibitem[Ronneberger et~al.(2015)Ronneberger, Fischer, and
  Brox]{ronnebergerUNetConvolutionalNetworks2015}
Olaf Ronneberger, Philipp Fischer, and Thomas Brox.
\newblock U-{{Net}}: {{Convolutional Networks}} for {{Biomedical Image
  Segmentation}}.
\newblock \emph{arXiv:1505.04597 [cs]}, May 2015.

@@

\bibitem[Tan et~al.(2020)Tan, Pang, and
  Le]{tanEfficientDetScalableEfficient2020}
Mingxing Tan, Ruoming Pang, and Quoc~V. Le.
\newblock {{EfficientDet}}: {{Scalable}} and {{Efficient Object Detection}},
  July 2020.

>>>>

\bibitem[Lin et~al.(2017)Lin, Doll{\'a}r, Girshick, He, Hariharan, and
  Belongie]{linFeaturePyramidNetworks2017}
Tsung-Yi Lin, Piotr Doll{\'a}r, Ross Girshick, Kaiming He, Bharath Hariharan,
  and Serge Belongie.
\newblock Feature {{Pyramid Networks}} for {{Object Detection}}.
\newblock \emph{arXiv:1612.03144 [cs.CV]}, April 2017.
\newblock \doi{10.48550/arXiv.1612.03144}.

\bibitem[Lin et~al.(2018)Lin, Goyal, Girshick, He, and
  Doll{\'a}r]{linFocalLossDense2018}
Tsung-Yi Lin, Priya Goyal, Ross Girshick, Kaiming He, and Piotr Doll{\'a}r.
\newblock Focal {{Loss}} for {{Dense Object Detection}}.
\newblock \emph{arXiv:1708.02002 [cs.CV]}, February 2018.
\newblock \doi{10.48550/arXiv.1708.02002}.

\bibitem[Liu et~al.(2021)Liu, Sharma, Park, Kenesei, Miceli, Almer, Kettimuthu,
  and Foster]{liuBraggNNFastXray2021}
Zhengchun Liu, Hemant Sharma, Jun-Sang Park, Peter Kenesei, Antonino Miceli,
  Jonathan Almer, Rajkumar Kettimuthu, and Ian Foster.
\newblock {{BraggNN}}: {{Fast X-ray Bragg Peak Analysis Using Deep Learning}}.
\newblock \emph{arXiv:2008.08198 [cs, eess]}, June 2021.
\newblock \doi{10.48550/arXiv.2008.08198}.

@@

\bibitem[Oktay et~al.(2018)Oktay, Schlemper, Folgoc, Lee, Heinrich, Misawa,
  Mori, McDonagh, Hammerla, Kainz, Glocker, and
  Rueckert]{oktayAttentionUNetLearning2018}
Ozan Oktay, Jo~Schlemper, Loic~Le Folgoc, Matthew Lee, Mattias Heinrich,
  Kazunari Misawa, Kensaku Mori, Steven McDonagh, Nils~Y. Hammerla, Bernhard
  Kainz, Ben Glocker, and Daniel Rueckert.
\newblock Attention {{U-Net}}: {{Learning Where}} to {{Look}} for the
  {{Pancreas}}.
\newblock \emph{arXiv:1804.03999 [cs.CV]}, May 2018.
\newblock \doi{10.48550/arXiv.1804.03999}.

@@

\bibitem[Ronneberger et~al.(2015)Ronneberger, Fischer, and
  Brox]{ronnebergerUNetConvolutionalNetworks2015}
Olaf Ronneberger, Philipp Fischer, and Thomas Brox.
\newblock U-{{Net}}: {{Convolutional Networks}} for {{Biomedical Image
  Segmentation}}.
\newblock \emph{arXiv:1505.04597 [cs]}, May 2015.
\newblock \doi{10.48550/arXiv.1505.04597}.

@@

\bibitem[Tan et~al.(2020)Tan, Pang, and
  Le]{tanEfficientDetScalableEfficient2020}
Mingxing Tan, Ruoming Pang, and Quoc~V. Le.
\newblock {{EfficientDet}}: {{Scalable}} and {{Efficient Object Detection}}.
\newblock \emph{arXiv:1911.09070 [cs.CV]}, July 2020.
\newblock \doi{10.48550/arXiv.1911.09070}.
